---
title: "Project Report (vignette)"
output:
  rmarkdown::html_vignette: default
  rmarkdown::pdf_document: default
vignette: |
  %\VignetteIndexEntry{project-report-vignette} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#devtools::install()
library(tibble)
library(leafart) 
#devtools::build_vignettes()
# To actually show the knitted vignette document, I had to use devtools::build_vignettes() and then remove the doc file from the .gitignore. 
# also using pdf_document instead of html_vignette
```


## Complete example

```{r}
get_params(nleaves = 1,
           split = 3,
           angle = c(-150,0,0,150),
           scale = c(.8,.9),
           n_layer = 5) %>% 
  create_leaf_pile() %>% 
  plot_leaves()

```

## Motivation 




## Growing a leaf: 

A leaf starts with a stalk. We keep track of the stalk start and endpoint, and then draw a line between them. 

Here's a stalk: 

```{r}
(initial_leaf <- tibble::tibble(
    x_0 = 0, y_0 = 0,
    x_1 = 0,y_1 = 1))
```

This format makes it harder to plot. The function `rake_leaves()` will transform the leaf into something better suited to plotting. The `plot_leaves()` function will plot a leaf after it is "raked"

```{r}
(rake_leaves(initial_leaf))

rake_leaves(initial_leaf) %>% 
  plot_leaves()
```

We consider this initial stalk to be the first "layer"

Now lets create some branches. The way the leaf/tree branches depends on the parameter values we pass to the growing function. These parameters could be single values, or a vector of values to be sampled from. 

We need to know the number of branches to branch off from, the angle to branch, and how long the new branches should be. 

The function `get_params()` will give us a list of parameter values. We can specify what values we want, or we can use its defaults. It will default to making one tree. Since we just want to make a tree with 1 additional layer now, we will also specify that. 

```{r}
params <- get_params(n_layer = 1,
                     scale = .5,
                     angle = 90,
                     split = 2)
```


To grow one branch, we use the function `one_branch()`. This function creates a new list that contains the growth of the new branch. Note the initial stalk also keeps track of some initial angle values. 

```{r}
initial_leaf <- tibble::tibble(
    x_0 = 0,
    y_0 = 0,
    x_1 = x_0,
    y_1 = y_0 + 1,
    angle = 90,
    length = 1L,
    iter_n = 1L
  )

one_branch(initial_leaf, params)

```

To grow all the branches in this second layer we use the function `grow_leaf_layers()`. This combines each branch (row) into one data frame that contains one row per new branch. 

```{r}
grow_leaf_layers(initial_leaf,params)
```

The function `grow_leaf()` will do this entire process, creating the initial stalk and growing the new layer (depending on the parameters)

```{r}
small_leaf <- get_params(n_layer = 1,
                     scale = .5,
                     angle = 90,
                     split = 2) %>% 
  grow_leaf()
```


And again, we have to clean up the data frame to be easier to plot. We now also have to keep track of which layer the branch belongs to so the graphing knows which points to connect. 

```{r,  out.width="50%"}
get_params(n_layer = 1,
                     scale = .5,
                     angle = 90,
                     split = 2) %>% 
  grow_leaf() %>% 
  rake_leaves()


get_params(nleaves = 1,
           n_layer = 2,
           scale = .5,
           angle = 90,
           split = 2) %>% 
  grow_leaf() %>% 
  rake_leaves() %>% 
  plot_leaves()
```


Now we have two layers. We repeat this growing process at the endpoint of each newly grown branch, until we have fully grown out the tree. 




## Attempts at speeding up runtime 

Creating and plotting the leaves will take a moment to run, especially if we are creating many leaves which each have many layers. I tried to improve this runtime . This exploration can be found in the document (here)[/../]

## Tests 

## Examples 

Examples of running this code can be found in the package README. All functions have associated help pages created from roxygen. Users can also utilize the shiny app to explore the code as well. 
