---
title: "Timing test"
author: "Emily Palmer"
date: "12/1/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
devtools::load_all()
```


# Check which method is faster 

```{r}
# With default parameters, number of leaves 10, ndistinct 6
bench::mark(
  fewer_distinct = {get_gingko_params(init_location = "origin") %>% 
  spread_leaves() },
  more_distinct = {get_gingko_params(init_location = "random") %>%
  grow_leaf() %>% 
  rake_leaves()},
  check = FALSE
)



bench::mark(
  fewer_distinct = {get_gingko_params(init_location = "origin", nleaves = 50, ndistinct = 3) %>% 
  spread_leaves() },
  more_distinct = {get_gingko_params(init_location = "random",nleaves = 50) %>%
  grow_leaf() %>% 
  rake_leaves()},
  check = FALSE
)
```

We have two methods to create a scatter of leaves. The first, randomly places the leaves, and has to create more distinct leaves. The second generates creates fewer distinct trees, and replicates the existing trees

Even with many leaves, and few distinct leaves, the randomly placing each new leaf method is much faster.

I would have thought that creating fewer trees and replicating and moving those leaves would have had a time improvement, but apparently not. 

Still this second method is useful if I ever want to add on to this project by adding animation for wind, which would need move and rotate methods to move the leaves. 
